Future challenges for Research Software Engineering

### 2025-09-28 correspondence/rebuttal.md

> Keywords could be richer

Thank You, we added some more keywords.

> "In order to structure the discussion, we decided to consider...". Was the discussion structured as presented or is the paper structured as presented; the sentence implies the former. Is there a rationale why the authors include the following topics? Have there been other topics in discussion that have not been namend in the paper?

Thanks for bringing this up. We have clarified this, that the workshop was an open discussion with some prepared questions.
We also explain how the questions have been rooted in some of the discussions of the teachingRSE project.

@@

> Page 3
> Story 1: In order to give a more concrete setting, imagine a world ten years from now. Not too overwhelmingly far ahead in the future, but distant enough for some changes to have occurred. – These are both incomplete sentences, ie it's a group of words that doesn't express a complete thought and is missing a necessary element, like a subject or a verb.

We have reworded this sentence in order to provide more natural british english.

> Page 4
> RSEng-relevant open educational resources and Master’s programmes are tracked in the Learning and Teaching RSE database2 and UK SSI resources hub3. The Carpentries now offer specialised software workshops for data scientists4, librarians5, and soon HPC practitioners6. – This seems to be about the future state, but it’s not clear what “now” means here (probably 2035?) – for example, a few paragraphs earlier there is wording “This means, that today’s workshop content of proper versioning and data management could become obsolete by using more intuitive tools.” – where today means 2025. Can it be made clearer throughout the paper when the text is talking about 2025 versus 2035?

Since the inconsistent use of times was mentioned by multiple reviewers, we went over the paper multiple times to be more consistent with regard to the use of tenses.
